=== am ende quasi requirements (ist, soll)===

- Neural networks. Is there a pattern how to  generate the neural network? Should it grow on its own? What type of neural network do we need?

- Stress level. Is there already something like the stress level algorithm. Growth of stress level. Can set up a algorithm that builds the perfect stress level for certain inputs? On what level do we have to set up the stress level calculation? Maybe whole streets? What parameters go into the algorithm? Limits for stress levels for the switching of the lights. Can we stick to the idea of green waves with our stress level algorithm? Can we explicitly make green waves? Is our algorithm better than a static signal wiring, if we just calculate it with perfect predictions? How much worse does it get if the predictions are off? Can we make the algorithm even better after we did the calculation examples. Idea: We should probably split off our stress level calculator to be able to monitor other signal wirings. I think the stress level growth algorithm really has to be more or less perfect. It is our metric to determine later if our prototype is better than existing solutions. Maybe compare signal wirings that we know are better and worse with the stress level algorithm and show empirically that our algorithm is good. Does the stress level approach have disadvantages? Are there other metrics? Maybe this and the neural networks stuff have to be seperate chapters? This would also make the titling of the chapters less generic, which I think is good and the work could be split up effectively. Maybe the system deciding on the signals that should be changed can not even find the optimal solution in reasonable time. The system is split up in two phases one that calculates stress levels and one that the signals. Maybe the calculation of the stress levels should even work with events in the end. When a traffic light switches from red to green it sends events to the next node and then the new stress level calculation for the traffic light is executed. This is too detailed for this chapter, but I think the idea is good.

- Exploration of different street crossings. Maybe in the sense of inputs for a neural network, because the input nodes and stuff should be generated by the application for every possible crossing. Are there especially challenging street crossings to implement? Does there have to be different stress level algorithms for different crossings?

